\chapter*{Acknowledgements}

We are grateful to all who supported the AI4PDPA project throughout Term 7.

From AsiaCloud Solutions, we extend our appreciation to Mr. Ng Lye Kiat for his trust, openness, and flexibility, which enabled the team to exercise meaningful autonomy in architectural and budgeting decisions. His support created the conditions for thoughtful exploration and well-grounded technical planning. We also thank Mr. Yuri See, our primary point of contact and subject matter expert, whose practical insights, clear expectations, and steady encouragement were consistently valuable. His guidance on real-world compliance considerations contributed significantly to our understanding of the PDPA landscape. Our gratitude further goes to Ms. Valerie Ng, whose reliable presence during meetings and dedicated support behind the scenes ensured smooth coordination and collaboration throughout the term.

From the Singapore University of Technology and Design, we express our sincere appreciation to Dr. Sun Zhu for her steady guidance, clarity, and structured feedback. Her timely advice helped us avoid premature implementation and focus on rigorous exploration, planning, and architectural grounding. Her mentorship played a central role in shaping AI4PDPA into a coherent and feasible project. We also thank Dr. Thomas Schroepfer for his constructive feedback during presentations and reviews. His external perspective strengthened our communication, problem framing, and justification of design choices. Finally, we acknowledge Dr. Susan Wong, whose support from the Centre for Writing and Rhetoric enhanced the quality of our written deliverables. Her guidance on report structure, clarity, and professional expression helped refine our communication as a team.

The team is deeply grateful to all who contributed their expertise, time, and guidance in supporting the meaningful progress of AI4PDPA during Term 7.
