\documentclass{class}

\title{-}
\author{-}
\date{-}

\renewcommand{\bibname}{References}
\DefineBibliographyStrings{english}{bibliography = {References}}

\begin{document}

\pagenumbering{roman}

\include{cover}
\include{acknowledgements}
\include{summary}

\tableofcontents

\clearpage

\pagenumbering{arabic}

\include{1-introduction}
\include{2-literature}
\include{3-design}
\include{4-implementation}
\include{5-validation}
\include{6-conclusion}

\printbibliography

\appendix

\chapter{Supplementary Material}
\label{app:supplementary-material}

\section{Rational Utility}
\label{app:rational-utility}

Rational Utility, as defined by
\[
	U_\text{rational}
	=
	440A
	+
	220\left(
		\frac{20}{P+7.43}
	\right)^{0.7}
	+
	400M^{0.3}
	+
	180\left(
		\frac{1}{1+T\exp(T-3)}
	\right)
\]
decomposes into four objective components: accuracy, price, multimodality, and latency.
Each term is a transformed version of a measured quantity, scaled by a contribution constant chosen from prior work on customer intention, loyalty, or adoption.
The transformation shape and constant together determine how strongly that quantity influences the final score and where diminishing returns begin.

The first term captures accuracy.
Here $A\in\mathbb{R}_{[0,1]}$ is the empirical accuracy of a model on an evaluation dataset.
Its contribution is scaled using the largest constant in the framework, reflecting findings that accuracy is the strongest predictor of user intention and retention in service environments \parencite{alhattami2025}.
In the context of legal and compliance assistance, factual correctness is especially critical, so accuracy is treated as the dominant factor.
Full accuracy yields the maximum contribution allocated to this dimension, while partial accuracy reduces the score proportionally.

The second term captures pricing utility.
Here, $P$ is the price per million tokens of combined input and output, as listed on OpenRouter.
The functional form is decreasing in $P$: as a model becomes more expensive to run, its contribution to Rational Utility falls.
The exponent induces diminishing sensitivity, so large price differences at the low end matter more than equally large differences at the high end, consistent with behavioural findings on price elasticity.
The contribution constant is derived from reported beta sensitivities for price effects on customer concentration, and is capped such that pricing cannot contribute more utility than accuracy \parencite{tanantong2024}.
This ensures that an extremely cheap but inaccurate model does not outrank a moderately priced, highly accurate one.

The third term measures the benefit of multimodality.
Here, $M$ is the number of input modalities, as listed on OpenRouter.
Empirical work suggests that the availability of additional interaction channels modestly improves customer engagement and concentration \parencite{zhang2024}.
We encode this with a sublinear exponent, which yields strong gains from adding the first few modalities but quickly introduces diminishing returns.
The contribution constant reflects an upper bound comparable to, but slightly below, the weight of accuracy, acknowledging that modality breadth is valuable but should not overshadow factual performance.

The final term reflects latency utility.
Here, $T$ is the latency in seconds, as listed on OpenRouter.
The chosen functional form behaves similarly to a squashed inverse curve: utility is high and near-saturated for low latencies, then declines sharply as response times exceed a few seconds, and eventually flattens out for very slow models.
This shape aligns with user studies showing that delays beyond a small threshold significantly degrade perceived quality and willingness to continue using a system, while shaving off sub-second latency yields smaller marginal gains \parencite{kim2024}.
The contribution constant is calibrated from reported beta sensitivities for time-related service attributes, using the mid-range estimate as a compromise between different studies.

Together, these four terms produce a composite Rational Utility score that balances factual quality, cost, interaction richness, and responsiveness.
The relative magnitudes of the contribution constants ensure that accuracy remains primary, while still rewarding models that are affordable, multimodal, and fast enough to support practical SME workflows.

\section{Budget Summary}
\label{app:budget-summary}

We used the \href{https://calculator.aws/#/estimate?id=f3936da1c288edd9947a25383f2b1e58731e93eb}{AWS Pricing Calculator} to determine the infrastructure budget allocation.

\end{document}
